\begin{longtable}{ll}
	{\bf\LARGE Acronyms and Abbreviations} & \\\\
	Acronym/Abbreviation & Definition \\
	CBF & Correlator Beamformer \\
	CDR & Critical Design Review \\
	ECP & Engineering Change Proposal \\
	ICD & Interface Control Document/Drawing \\
	N/A & Not Applicable \\
	NRF & National Research Foundation \\
	QA  & Quality Assurance \\
	QTP & Qualification Test Procedure \\
	QTR & Qualification Test Report \\
	SE  & System Engineer \\
	TBC & To Be Confirmed \\
	TBD & To Be Determined \\
	TL  & Team Leader \\
	TRR & Test Readiness Review \\
\end{longtable}

\chapter{Introduction and Scope}
\section{Identification}
This Qualification Test Procedure document describes the qualification tests to be executed on the {\bf M1200-0000} Correlator-Beamformer of the MeerKAT Radio Telescope for Functional Releases.

This QTP only covers tests that test and qualify critical aspects of the Correlator-Beamformer.

\section{Version Information}
\subsection{Hardware identification}
For each Functional Release, the Correlator-Beamformer is deployed using the SKARAB hardware platform. Hardware to be utilized during qualification shall be identified prior to testing. The exact hardware configuration - including SKARAB boards, network switches and servers - employed for each run of this qualification test procedure shall be available in the applicable Qualification Test Reports.
\subsection{Software/firmware release information}
Software, gateware and firmware versions to be utilized during qualification shall be identified prior to testing. The list of software, firmware, and gateware items, and their respective versions, employed for this Correlator-Beamformer Functional Release Qualification shall be made available in the Qualification Test Reports.

Following qualification, formal release notes and software data packs for the Correlator-Beamformer software, gateware and firmware shall be released.
\section{Context}
This document categorises all tests according to Verification Events. Each Verification Event employs a test that fulfills a Verification Requirement. Each Verification Requirement, in turn, verifies one or more requirements. A single Verification Event, or test, may thefore verify multiple requirements.

This document captures all CBF requirements, regardless if they are applicable to the Array Release under test or not. The Resulting Qualification Test Reports will indicate which requirements are not tested. All tests in this QTP shall be executed for each CBF instrument that is available during the Array Release under test. A separate Qualification Test Report shall be produced for each CBF intrument tested and qualified.
\section{Purpose}
This document forms part of a set of Qualification Test Procedures (QTPs) for the CBF. The complete set of CBF QTPs document the test procedures required to verify that the CBF meets specification.
The resultant Qualification Test Report (QTR), together with the QTRs from other CBF Qualification Events, will be reviewed at the Critical Design Review (CDR) of the CBF.
\chapter{Applicable and Reference Documents}
\section{Applicable Documents}
The following documents are applicable to the extent specified herein. In the event of conflict between the contents of the applicable documents and this document, the applicable document shall take precedence.  Nothing in this document supersedes applicable laws and regulations.
\newline\newline
[1]\hspace{10mm} T. van Balla, {\bf M1200-0000-000}, Rev 4, {\it Correlator-Beamformer Requirement Specification}, January 22, 2018.
\section{Reference Documents}
The following documents are referenced in this document and are merely listed for convenience.\newline\newline
\hspace{10mm}None.
