\begin{longtable}{ll}
	{\bf\LARGE Acronyms and Abbreviations} & \\\\
	Acronym/Abbreviation & Definition \\
	CBF & Correlator Beamformer \\
	CDR & Critical Design Review \\
	ECP & Engineering Change Proposal \\
	ICD & Interface Control Document/Drawing \\
	N/A & Not Applicable \\
	NRF & National Research Foundation \\
	QA  & Quality Assurance \\
	QTP & Qualification Test Procedure \\
	QTR & Qualification Test Report \\
	SE  & System Engineer \\
	TBC & To Be Confirmed \\
	TBD & To Be Determined \\
	TL  & Team Leader \\
	TRR & Test Readiness Review \\
\end{longtable}

\chapter{Introduction and Scope}
\section{Identification}
This document describes the Qualification Test Report (QTR) for the Correlator-Beamformer Test Prodcedure for Array Release 2 and 3 as described in [2].\newline

All CBF functionality, for AR2/3, is tested in this release. Functionality made available for AR2/3 is detailed in M1200-0000-001 Correlator-Beamformer Development Plan [1]. This release is provided for deployment of a AR2/3 to site with full functionality. Array Release 2 and 3 shall be treated as formal baselines for the Correlator-Beamformer Subsystem.\newline

This particular Qualification Test Report {\bf (M1200-0000-055-1)} describes the results of all test procedures relating to an {\bf 4 Antenna System running in Wideband Coarse (4K) mode with a beamformer \it{(bc8n856M4k)}}.
\subsection{Hardware identification}
For Array Release 2 and 3, the Correlator-Beamformer is deployed using the SKARAB hardware platform. The exact hardware configuration - including SKARAB boards, network switches and servers - employed for testing is described in this Qualification Test Report.
\subsection{Software/firmware release information}
The list of software, firmware, and gateware items, and their respective versions, employed for the Correlator-Beamformer Array Release 2/3 Qualification is described this Qualification Test Report.

Following qualification, formal release notes and software data packs for the Correlator-Beamformer software, gateware and firmware shall be released.
\section{Context}
This document categorises all tests according to Verification Events. Each Verification Event employs a test that fulfills a Verification Requirement. Each Verification Requirement, in turn, verifies one or more requirements. A single Verification Event, or test, may thefore verify multiple requirements.

Each Verification Event section presents the results of the test run during the particular Verification Event for the CBF bc8n856M4k under test.
\section{Purpose}
This document forms part of a set of Qualification Test Reports (QTRs) for the CBF. The complete set of CBF QTRs documents the results of the qualification test procedures required to verify that the CBF meets specification. The QTRs generated during qualification of Array Release 2/3 shall form part of the Qualification Baseline Document Pack of CBF for Array Release 2 and 3.\newline

This Qualification Test Report (QTR), together with the QTRs from other CBF Qualification Events, will be reviewed at the Critical Design Review (CDR) of the CBF.
\chapter{Applicable and Reference Documents}
\section{Applicable Documents}
The following documents are applicable to the extent stated herein. In the event of conflict between the contents of the applicable documents and this document, the applicable documents shall take precedence:\newline\newline
[1]\hspace{10mm} T. van Balla, {\bf M1200-0000-001}, Rev 3, {\it MeerKAT Correlator-Beamformer Development Plan}, 04 December 2017\newline\
\section{Reference Documents}
The following documents are referenced in this document. In the event of conflict between the contents of the referenced documents and this document, this document shall take precedence:\newline\newline
[2]\hspace{10mm} T. van Balla, {\bf M1200-0000-054}, Rev 1, {\it MeerKAT Correlator-Beamformer Array Release 2/3 Qualification Test Procedure}\newline

